---
title: "Class Problem"
format: html
editor: visual
---

# Get 500 samples of 100 observations from Auto, build regression and plot the distribution of the coefficients.

## Loading the packages

```{r}
#| warning: false

library(ISLR2)
library(tidyverse)
```

creating an empty list to store samples & generating 500 samples and saving them as individual lists withib the list

```{r}
sample_list <- list()

for(i in 1:500) { sample_list[[i]] <- sample_n(Auto, 100) }
```

Repeating the same to get the estimators. I am saving the extracted coefficients in a dataframe to make it more user friendly for me. I am more comfortable with dataframe. I know I saved it as a list first but its ok as long as my code works.

```{r}

estimators <- list()

for (i in 1:length(sample_list)) {
  sample_data <- data.frame(sample_list[[i]])
  m <- lm(horsepower ~ weight, data = sample_data)
  estimators[[i]] <- m$coefficients
  estimators <- data.frame(matrix(unlist(estimators), ncol = length(estimators), byrow = FALSE))
}
```

Df estimators has 500 columns(from the 500 samples) and has two rows, first row is the intercept and second is the slope
```{r}
#| echo: true

head(estimators)[1:5]
```

Transposing the dataframe and naming the cols as their respective coeff name.

```{r}
coeffx <- data.frame(t(estimators))
colnames(coeffx)[1] <- "intercept"
colnames(coeffx)[2] <- "slope"
```

```{r}
head(coeffx, 5)
```

FINALLY, plotting the coeffs distribution. I didnt remember which one we had to plot so i did both.

```{r}
#| echo: true

plot(density(coeffx$intercept), main = "Density Plot of Intercept Coeff")
plot(density(coeffx$slope), main = "Density Plot of Slope Coeff")
```
I dont remember the instructions so I also found out the averages of the coeffs.

```{r}
#| echo: true

mean(coeffx$intercept)
mean(coeffx$slope)
```
